---
title: "HW3"
author: "Michael Tieu"
date: "9/15/2018"
output: 
  html_document:
    keep_rmd: true
---

# Question 1: GitHub Cloning
### Git Command Code:
```{r}
#cd documents
#cd Projects
#cd MSDS6306
#mkdir MSDS6306HW3
#git clone https://github.com/awesomedata/awesome-public-datasets
```

# Question 2: Data Summary
### a) Assigning the dataframe
```{r}
df <- read.csv('titanic.csv', header=TRUE)
```

### b) Output of respective females and males aboard the Titanic
```{r}
table(df$Sex)
barplot(table(df$Sex),main="Number of Females and Males Aboard Titanic", xlab="Gender",ylab="Count")
```

### c) Using apply function to output means of Age, Fare, Survival
```{r}
df2 <- df[,c(2,6,10)]
sapply(df2,mean,na.rm=TRUE)
```

# Question 3: Sleep Data
### Parts a) through d):
```{r} 
Question3 <- function(x)
{
  medianAge <- median(x$Age,na.rm=TRUE)
  MinSleep <- min(x$Duration, na.rm = TRUE)
  MaxSleep <- max(x$Duration, na.rm = TRUE)
  MeanRSES <- mean(x$RSES, na.rm = TRUE)
  sdRSES <- sd(x$RSES, na.rm = TRUE)
  report <- data.frame(MedianAge=medianAge, SelfEsteem=MeanRSES/5, SE_SD=sdRSES/5, DurationRange=MaxSleep-MinSleep)
  return(round(report, digits=2))
}
```

### e)
```{r}
sleep<- read.csv('sleep_data_01.csv')
Question3(sleep)

```

# Question 4: FiveThrtyEight
### a) Install the fivethirtyeight package
```{r}
#install.packages("fivethirtyeight")
```

### b) Assign 22nd dataset to df
```{r}
library(fivethirtyeight)
df <- (college_recent_grads)
```

### c) Comment the related news story
```{r}
#https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
```

### d) Give dimensions and column names of the dataframe
```{r}
dim(df)
colnames(df)
```

# Question 5: Data Summary
### a) Give the column names of the dataframe and number of columns but not rows
```{r}
colnames(df)
ncol(df)
```

### b) Generate count of each unique major_category in a dataframe
```{r}
library(plyr)
Major_Cat <- sapply(df$major_category,unique)
Major_Count <- count(Major_Cat)
```

### c)
```{r}
par(las=2)
barplot(Major_Count$freq, names.arg=Major_Count$x,horiz=TRUE, main="Frequency of College Majors",col='blue',xlab="Frequency",ylab="Majors",cex.names=0.3,space=0.3,cex.axis=0.75)
```

### d) Write fivethirtyeight data to csv file
```{r}
write.csv(df,"FiveThirtyEight_CollegeGradData.csv", row.names=F)
```


# Quetion 6: Codebook
### a) Start a new repo on GitHub for MSDS homework
```{r}
#cd documents
#cd projects
#mkdir MSDS_HW
#cd MSDS_HW
#git init
```

### b) Create README.md 
```{r}
#echo 'This contains homework in class sections MSDS6371 and MSDS6306. For questions, contact mtieu@smu.edu' > README.md
#echo 'Sources for datasets and other external references will be provided in the appropriate folder.' >> README.md
#mkdir MSDS6306_FiveThirtyEight
```

### c) Posting Rmd script, HTML, FiveThirtyEight data + README credit
```{r}
#cd MSDS6306_FiveThirtyEight
#echo 'This folder contains my answers to the MSDS6306 Unit 3 Assignment.' > README
#echo 'All sleep data was provided.' >> README
#echo 'External data was extracted from the FiveThirtyEight source linked below.' >> README
#echo 'https://github.com/rudeboybert/fivethirtyeight' >> README

#cd ..
#cd ..
#cd MSDS6306
#cd MSDS6306HW3
#mv MSDS6306_HW3.Rmd /users/mtieu/documents/Projects/MSDS_HW/MSDS6306_FiveThirtyEight
#mv FiveThirtyEight_CollegeGradData.csv /users/mtieu/documents/Projects/MSDS_HW/MSDS6306_FiveThirtyEight
#cd ..
#cd ..

#HTML was not manually moved; I knit the file after completing HW.

#cd MSDS_HW
#git commit -m "first commit"
#git remote add origin https://github.com/emteepastiche/MSDS_HW.git
#git add README
#git add MSDS6306_FiveThirtyEight/
#git commit -m "first commit"
#git push -u origin master
```

### d) Link to GitHub
```{r}
#https://github.com/emteepastiche/MSDS_HW
```