---
title: "HW3"
author: "Michael Tieu"
date: "9/15/2018"
output: 
  html_document:
    keep_rmd: true
---

# Question 1: GitHub Cloning
### Git Command Code:
```{r}
#cd documents
#cd Projects
#cd MSDS6306
#mkdir MSDS6306HW3
#git clone https://github.com/awesomedata/awesome-public-datasets
```

# Question 2: Data Summary
### a) Assigning the dataframe
```{r}
df <- read.csv('titanic.csv', header=TRUE)
```

### b)
```{r}
table(df$Sex)
plot(table(df$Sex),main="Number of Females and Males Aboard Titanic", xlab="Gender",ylab="Count")
```

### c)
```{r}
df2 <- df[,c(2,6,10)]
sapply(df2,mean,na.rm=TRUE)
```

#Question 3: Sleep Data
### Parts a) through d):
Question3 <- function(x)
{
  medianAge <- median(x$Age,na.rm=TRUE)
  MinSleep <- min(x$Duration, na.rm = TRUE)
  MaxSleep <- max(x$Duration, na.rm = TRUE)
  MeanRSES <- mean(x$RSES, na.rm = TRUE)
  sdRSES <- sd(x$RSES, na.rm = TRUE)
  report <- data.frame(MedianAge=medianAge, SelfEsteem=MeanRSES/5, SE_SD=sdRSES/5, DurationRange=MaxSleep-MinSleep)
  return(round(report, digits=2))
}

# Question 4: FiveThrtyEight
### a)
```{r}
install.packages("fivethirtyeight")
```

### b)
```{r}
df <- (college_recent_grads)
```

### c)
```{r}
#https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
```

### d)
```{r}
dim(df)
colnames(df)
```

# Question 5: Data Summary
### a)
```{r}
colnames(df)
ncol(df)
```

### b)
```{r}
Major_Cat <- sapply(df$major_category,unique)
Major_Count <- count(Major_Cat)
```

### c)
```{r}
par(las=2)
barplot(Major_Count$freq, names.arg=Major_Count$x,horiz=TRUE, main="Frequency of College Majors",col='blue',xlab="Frequency",ylab="Majors",cex.names=0.3,space=0.3,cex.axis=0.75)
```

### d)
```{r}
write.csv(df,"FiveThirtyEight_CollegeGradData.csv", row.names=F)
```

cd documents
cd projects
mkdir MSDS_HW
cd MSDS_HW
git init

Michaels-MBP:msds_hw mtieu$ echo 'This contains homework in class sections MSDS6371 and MSDS6306. For questions, contact mtieu@smu.edu' > README
Michaels-MBP:msds_hw mtieu$ echo 'Sources for datasets and other external references will be provided in the appropriate folder.' >> README
